Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-14 Ben_Manuscripts/structure_paper/Draft.tex
reorganization

  \subsection{Density of monomers around pores}

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K in the ordered and disordered
  basins. We generated simulated patterns using the equilibrated portion of each 
  simulation trajectory. The patterns for all structures are shown and compared to
  experiment in Figure~\ref{fig:XRDsim}.
  %MRS10: Would be btter to lead with something describing what we found, not a caveat, just for clarity. Might belong better in the previous paragraph if left here, since it is a clarifying point that should be communicated, not an actual finding.
  The diffraction patterns show some noise, especially along the axis where $q_r$=0. There are
  two main reasons for this noise. First is that we angle averaged the 3D structure factor 
  (see section~\ref{method:xrd}) which inherently gives less data as $q_r$ approaches 0. Second, 
  our simulations are not long enough to sample enough truly independent configurations within
  their respective metastable basins. By sampling more uncorrelated equilibrium configurations,
  we can suppress some of the noise (See section S-\ref{S-section:xrd_noise}).

  \begin{figure}[!htb]
	\centering
	\begin{subfigure}{0.88\textwidth}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
			\end{subfigure}
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
			\end{subfigure}

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  %MRS10: would domain misalignment make a difference in itensity?  I though we decided it wouldnt (it would more broaden?).
  %You can talk about how you WILL analyze the intensity diffence later on, that it doesn't need to be analyzed here.
  % MRS4: comments from Matt suggest that domain misalignment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
  maximum at $q_z < 1.5~\AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
  rather than 3.7 \AA. R-double does not appear in any of the patterns.

@@

  The simulated XRD patterns of the parallel displaced configurations show additional
  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
  for the same reason as R-double. It is possible that parallel displaced monomers contribute
  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.

@@

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
  %MRS10: weird transition between these two; it's a result that interrupts the discussion of methods.
  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
  identified spots based on visual inspection. 
  %MRS10: what criteria were used?  Need to provide what was used to make the decision.
If the spots were not easily discernible, then the 
  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
  R-$\pi$, as that is where it appears experimentally. The intensity of R-spots is slightly
  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
  agrees with experiment. There is no R-double intensity to be measured. %MRS10: specific where no R-double intensity was measured. None of the simulations, correct?
Figures are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements. %MRS10: Specify what figures clarify what things.  Also, use active voice in this section.

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}
  %BJC5: Bold font is caused by achemso document type
  %MRS7: huh.
  %BJC6: yea, specifically the one for j phys chem B. I compiled with a different document type and the captions looked normal
  There are clear differences between simulated and experimental results that must be addressed
  and justified. We will explore the possible origin of select experimental reflections and form 
  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
  want answer:  
  %MRS10: should the ``why is R-pi in not quite the right place'' be here, to have those sorts of questions more centralized?
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-double?
  \end{enumerate}

@@

  \subsubsection{The origin of R-spots}\label{section:rspots}
%MRS10: I rephrased the below, check the diffs.
  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K. Many force fields do not obtain the correct equilibrium structure at precisely the experimental temperature. Wang et al. highlighted the 
  shortcoming of some of the most popular protein force field in predicting the temperature
  dependence of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
  our membrane system, simulated at 300K, is overly structured compared to the experimental structure at 300K.
  We found that lowering the temperature better resolved the R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' temperature might indeed be too high, overstabilizing structure. 
%  The relative intensity 
%  of R-spots in this system is slightly higher than experiment (1.5 vs. 1.3)

@@

  Evidence 
%MRS10: added
from the simulations
  strongly suggests that the R-spots signal is not a result of alkane
  chain tilt. Previous literature has attributed the spots in this particular
%MRS10: clarified that it was THIS exact data, and not similiar images. Correct if wrong.
WAXS 
%pattern 
dataset
as the product of tilted alkane chains~\cite{feng_scalable_2014}.
  We measured the tilt angle of the alkane chains of the 280K system and showed
  that it equilibrates to an average tilt angle of
  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. 
  %MRS8: did you do a few different things here as sensitivity analysis to show that the finding was robust?  If so, putting some of that in would be useful.
  %BJC7: make it clear that it is the 280K. Reference all configurations where tilt angles were calculated.

@@

  %BJC9: I think Matt gets confused here. I put a more detailed explanation in 
  % the supplemental information. Do you think that's enough, or should I add
  % to this figure?
  %MRS10: rephrased.
  The evidence strongly suggests that R-spot pattern occurs because tails pack together hexagonally. 
  We plotted the center of masses of the 
  first four tail atoms of each tail originating from each head group 
  (Figure \ref{fig:centroids}). We measured the angle between each center of
  mass and its nearest neighbor center of masses with respect to the $xy$ 
  plane of the membrane. We see distinct peaks in the distribution of these 
  angles located ca. $-60\degree$, $0\degree$, and $60\degree$ which is 
  consistent with a hexagonally packed configuration 
  (Figure~\ref{fig:layered_tails}). 
  %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
This ordering dies off at the tail ends,
  where there is more space to fill causing them to pack nearly isotropically.
  See Section~S-\ref{S-tail_packing} for a more detailed explanation of the 
  calculation and packing distributions generated from different sections of
  the tails.

@@

  \subsubsection{Discrepancies between experimental and simulated R-$\pi$}\label{section:rpi}
  %MRS10: in the list of questions above, you just talk about intensity, but this title talks about more discrepnacies. It could go either way (as I mention before, there's the issue of R-pi placement, too), but it should be consistent.
  The experimentally measured R-$\pi$ is more intense relative to the experimental system. The difference in intensity
  ranges from 3 times too high in the ordered parallel displaced system to 15 times too 
  high in the ordered sandwiched configuration (Table~\ref{table:relative_inensities_300K}).
  %MRS10: should specify this is in the 300 K simulations.

@@

  An exact quantitative comparison between experiment and simulation is not feasible for several reasons. 
  Experimental peaks broaden due to effects that we can not easily simulate such
  as finite size crystalline domains and instrumental resolution. In our simulated
  XRD patterns, the system size imposes limitations on the resolution, which makes
  it difficult to reliably fit peaks. This is especially problematic when comparing
  the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental FWHM 
  (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
  Additionally, we model each atom with a Gaussian sphere of electron density. 
  The true electronic structure is likely much more complicated. 
  %MRS10: modified
  However, we can explore reasons for which differences in the simulation structure could changes the peak shapes to be in better agreement with experiment.

@@

%MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
%BJC9: hahaha^
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
  \caption{}\label{fig:sf_qy_nocorrelation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
  \caption{}\label{fig:sf_qy_correlation}
  \end{subfigure} 
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
  \caption{}\label{fig:sf_qz_correlation}
  \end{subfigure}   
  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
  points meant to represent monomer head groups. We added a similar amount of noise to 
  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
  peaks. (b) When we correlate the distance between points within each column, the 
  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
  intensity between the center and outer peaks. (c) Correlation of the distance between
  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
  \end{figure}

@@

@@

  \subsection{Slow dynamics}

>>>>

  \subsection{Density of monomers around pores}\label{section:mon_per_pore}

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K in the ordered and disordered
  basins. We generated simulated patterns using the equilibrated portion of each 
  simulation trajectory. The simulated diffraction patterns have some noise, especially
  along the $q_z$ axis at $q_r$=0. There are two main reasons for this noise. First
  is that we angle averaged the 3D structure factor (see section~\ref{method:xrd})
  which inherently gives less data as $q_r$ approaches 0. Second, we hypothesize that 
  the more important issue is that our simulations are not long enough to sample 
  enough truly independent configurations within their respective metastable basins
  (See section~\ref{section:slow_dynamics}). By sampling more uncorrelated equilibrium
  configurations, we can suppress some of the noise (See section S-\ref{S-section:xrd_noise}
  for a detailed example of this effect). The simulated patterns generated for all systems
  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.

  % BJC10: to be reformatted : add captions. Maybe shift experimental pattern to (a)
  % BJC10: be more terse in main caption. Add references to sections
  \begin{figure}[!htb]
	\centering
	\begin{subfigure}{0.88\textwidth}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
			\end{subfigure}
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
			\end{subfigure}

@@

  The simulated XRD patterns show moderate agreement with experiment. There 
  are key qualitative and quantitative differences between the experimental and simulated
  locations and intensities of each major reflection. We measured the intensity and location
   of each simulated reflection relative to its experimental counterpart 
  (Table~\ref{table:relative_inensities_300K}). Our methods for measuring the intensity of
  each reflection are presented in section S-\ref{S-section:xrd_intensities}. We have
  devoted individual subsections to explain each major reflection. We start with relatively 
  uncomplicated analyses of experimentally-similar reflections:
  %BJC10: Could make the following more descriptive. For example : "The location of R-alkanes", "The intensity of R-pores", "The origin of R-spots", "The shape and intensity of R-pi", "The origin of R-double". 
  \begin{itemize}
  	\item R-alkanes (section~\ref{section:ralkanes})
  	\item R-pores (section~\ref{section:rpores})
  \end{itemize}
  and then move onto more complicated explanations of those reflections whose characteristics
  do not match, or have not been fully explained by experiment:
  \begin{itemize}
  	\item R-spots (section~\ref{section:rspots})
  	\item R-$\pi$ (section~\ref{section:rpi})
  	\item R-double (section~\ref{section:rdouble})
  \end{itemize}

%  \begin{table}[h]
%  \centering
%  \begin{tabular}{c|cccccccccc}
%  \toprule
% 		   & \multicolumn{5}{c}{Configuration} \\
%  \hline
%           &\multicolumn{2}{c}{}            & \multicolumn{2}{c}{}          & \multicolumn{2}{c}{Parallel} & \multicolumn{2}{c}{Disordered} & \multicolumn{2}{c}{Disordered}         \\
%           & \multicolumn{2}{c}{Experiment} & \multicolumn{2}{c}{Sandwiched} & \multicolumn{2}{c}{Displaced} & \multicolumn{2}{c}{Sandwiched}  & \multicolumn{2}{c}{Parallel Displaced} \\
%  Reflection & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) \\
%  \midrule
%  R-alkanes  & 1.0  & 1.4  & 1.0  & 1.4 & 1.0 & 1.4 & 1.0 & 1.4 & 1.0 & 1.4  \\  
%  R-spots    & 1.3  & 1.4  & 1.3  & 1.4 & 1.2 & 1.4 & 1.1 & 1.4 & 1.2 & 1.4  \\
%  R-$\pi$    & 2.8  & 1.7  & 44.0 & 1.4 & 7.7 & 1.4 & 8.4 & 1.4 & 10.1& 1.4  \\
%  R-double   & 0.9  & 0.85 & --   &  -- & --  & --  & --  & --  &  -- & --   \\ 
%  \bottomrule
%  \end{tabular}
%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
%  does not appear in any patterns, and thus has no measurable intensity.}
%  \label{table:relative_inensities_300K} 
%  \end{table}

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\
  R-pores    & 12.3       &  49.5      &  54.0     & 50.8       & 53.4               \\
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

%    \begin{table}[h]
%  \centering
%  \begin{tabular}{c|ccccc}
%  \toprule
% 		   & \multicolumn{5}{c}{Configuration} \\
%  \hline
%             &\multicolumn{2}{c}{}     &            & Parallel  & Disordered & Disordered         \\
%  Reflection & \multicolumnExperiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
%  \midrule
%  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
%  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
%  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
%  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
%  \bottomrule
%  \end{tabular}
%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
%  does not appear in any patterns, and thus has no measurable intensity.}
%  \label{table:relative_inensities_300K} 
%  \end{table}

  %MRS10: would domain misalignment make a difference in itensity?  I though we decided it wouldnt (it would more broaden?).
  %You can talk about how you WILL analyze the intensity diffence later on, that it doesn't need to be analyzed here.
  % MRS4: comments from Matt suggest that domain misalignment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
%  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
%  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
%  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
%  maximum at $q_z < 1.5~\AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
%  rather than 3.7 \AA. R-double does not appear in any of the patterns.

@@

@@

%  We quantified the numerical discrepancies present when comparing the relative intensities
%  of each reflection of interest between experimental and simulated patterns. 
%  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
%  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
%  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
%  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
%  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
%  %MRS10: weird transition between these two; it's a result that interrupts the discussion of methods.
%  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
%  identified spots based on visual inspection. 
%  %MRS10: what criteria were used?  Need to provide what was used to make the decision.
%If the spots were not easily discernible, then the 
%  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
%  R-$\pi$, as that is where it appears experimentally. The intensity of R-spots is slightly
%  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
%  agrees with experiment. There is no R-double intensity to be measured. %MRS10: specific where no R-double intensity was measured. None of the simulations, correct?
%Figures are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements. %MRS10: Specify what figures clarify what things.  Also, use active voice in this section.

%  There are clear differences between simulated and experimental results that must be addressed
%  and justified. We will explore the possible origin of select experimental reflections and form 
%  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
%  want answer:  
%  %MRS10: should the ``why is R-pi in not quite the right place'' be here, to have those sorts of questions more centralized?
%  \begin{enumerate}
%	\item What is the origin of R-spots?
%	\item How can we modify our simulations to account for the discrepancies between the experimental and simulated R-$\pi$ peak.
%  	\item What is the origin of R-double?
%  \end{enumerate}

@@

  \subsubsection{R-alkanes}\label{section:ralkanes}

  R-alkanes appears close to its expected location. In all cases, the maximum intensity
  of R-alkanes appears at a $|\mathbf{q}|$ value slightly higher than experiment. 
  We expect that the exact location of R-alkanes will not be perfect in our simulations
  since the simulated diffraction patterns are interpolated between a finite number of
  bins in each frequency dimension. We can achieve higher resolution with a larger
  system size, however we are satisfied with the packing distances shown by our simulations.
  %BJC10: I could integrate a 3D correlation function to get a better value

  We believe that R-alkanes is the experimental feature most likely to be reproduced by
  our simulations. For this reason we normalized the experimental and simulated diffraction
  patterns so that the average intensity within the R-alkanes is equal to 1.

  \subsubsection{R-pores}\label{section:rpores}

   R-pores is about 4 times more intense than experiment in all simulated systems. 
   %BJC10: trying to come up with a good explanation.

   We are not concerned with exactly reproducing the intensity of R-pores since it is a 
   product of long distance correlation between pores. We are primarily concerned with
   the structure within pores which is better described by reflections at higher 
   $|\mathbf{q}|$ values. The location of R-pores \textit{is} important because we can 
   use it to learn the number of monomer columns within each pore as we did in 
   section~\ref{section:mon_per_pore}

  \subsubsection{The origin of R-spots}\label{section:rspots}
%MRS10: I rephrased the below, check the diffs.
  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K. Many force fields do not obtain the correct equilibrium structure
  at precisely the experimental temperature. Wang et al. highlighted the shortcoming of 
  some of the most popular protein force field in predicting the temperature dependence 
  of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
  our membrane system, simulated at 300K, is overly structured compared to the experimental
  structure at 300K. We found that lowering the temperature better resolved R-spots 
  (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' temperature might 
  indeed be too high, overstabilizing structure. 
%  The relative intensity 
%  of R-spots in this system is slightly higher than experiment (1.5 vs. 1.3)

@@

  Evidence from the simulations strongly suggests that the R-spots signal is not a 
  result of alkane chain tilt. Previous literature has attributed the spots in 
  this particular WAXS dataset as the product of tilted alkane chains~\cite{feng_scalable_2014}.
  We measured the tilt angle of the alkane chains of the 280K system and showed
  that it equilibrates to an average tilt angle of -2\degree~(Fig.~\ref{fig:tilt}),
  far from the 37\degree~tilt angle previously used to explain R-spots.

@@

  %BJC9: I think Matt gets confused here. I put a more detailed explanation in 
  % the supplemental information. Do you think that's enough, or should I add
  % to this figure?
  %MRS10: rephrased.
  The evidence strongly suggests that R-spot pattern occurs because tails pack 
  together hexagonally. We plotted the center of masses of the first four tail 
  atoms of each tail originating from each head group (Figure \ref{fig:centroids}).
  We measured the angle between each center of mass and its nearest neighbor 
  center of masses with respect to the $xy$ plane of the membrane. We see distinct
  peaks in the distribution of these angles located ca. $-60\degree$, $0\degree$,
  and $60\degree$ which is consistent with a hexagonally packed configuration 
  (Figure~\ref{fig:layered_tails}). 
  %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
  %BJC10: I only addressed this because Matt wanted a more thorough characterization of tail order 
This ordering dies off at the tail ends,
  where there is more space to fill causing them to pack nearly isotropically.
  See Section~S-\ref{S-tail_packing} for a more detailed explanation of the 
  calculation and packing distributions generated from different sections of
  the tails.

@@

  \subsubsection{Discrepancies between experimental and simulated R-$\pi$}\label{section:rpi}
  %MRS10: in the list of questions above, you just talk about intensity, but this title talks about more discrepnacies. It could go either way (as I mention before, there's the issue of R-pi placement, too), but it should be consistent.
  The simulated intensity of R-$\pi$ at 300K is more intense relative to the experimental 
  system. The difference in intensity ranges from 3 times too high in the ordered parallel
  displaced system to 15 times too high in the ordered sandwiched configuration 
  (Table~\ref{table:relative_inensities_300K}).
  %MRS10: should specify this is in the 300 K simulations.

@@

  An exact quantitative comparison between experiment and simulation is not feasible for several reasons. 
  Experimental peaks broaden due to effects that we can not easily simulate such
  as finite size crystalline domains and instrumental resolution. In our simulated
  XRD patterns, the system size imposes limitations on the resolution, which makes
  it difficult to reliably fit peaks. This is especially problematic when comparing
  the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental FWHM 
  (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
  Additionally, we model each atom with a Gaussian sphere of electron density. 
  The true electronic structure is likely much more complicated. However, we can
  explore reasons for which differences in the simulation structure could change
  the peak shapes to be in better agreement with experiment.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
  \caption{}\label{fig:sf_qy_nocorrelation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
  \caption{}\label{fig:sf_qy_correlation}
  \end{subfigure} 
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
  \caption{}\label{fig:sf_qz_correlation}
  \end{subfigure}   
  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
  points meant to represent monomer head groups. We added a similar amount of noise to 
  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
  peaks. (b) When we correlate the distance between points within each column, the 
  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
  intensity between the center and outer peaks. (c) Correlation of the distance between
  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
  \end{figure}

@@

  %BJC10: I think this belongs somewhere in this section.
  The simulated XRD patterns of the parallel displaced configurations show additional
  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
  for the same reason as R-double. It is possible that parallel displaced monomers contribute
  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.

@@

  \subsection{Slow dynamics}\label{section:slow_dynamics}
